You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-25 paper/paper.tex
some more writing...

After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.  The modern translations from each source are qualitatively quite
different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the enotes translations are much more conservative, making fewer changes.
To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
original text; the Sparknotes paraphrases result in a BLEU score of 23.67, whereas the Enotes paraphrases prouce a much higher BLEU of 49.60 indicating their similarity to the original text.
These corpus statistics are summarized in table \ref{corpus_stats}.

@@

\subsubsection{Dictionary Based Paraphrase}
Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.

@@

\subsection{Comparison Using Existing Automatic Evaluation Metrics}
Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=2.1in]{figures/bleupinc1.pdf} & \includegraphics[width=2.1in]{figures/bleupinc2.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.}
  \label{bleupinc}
\end{figure}

\begin{itemize}
  \item List the various systems we evaluate (e.g. varying LM size, etc...)
  \item Plot BLEU and PINC scores for the various systems
\end{itemize}

>>>>

After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.  The modern translations from each source are qualitatively quite
different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the enotes translations are much more conservative, making fewer changes.
To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases prouce a much higher BLEU of 52.30 indicating their similarity to the original text.
These corpus statistics are summarized in table \ref{corpus_stats}.

@@

\subsubsection{Dictionary Based Paraphrase}
\label{dictionary_baseline}
Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.

@@

\subsection{Comparison Using Existing Automatic Evaluation Metrics}
Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.  A summary of each system is presented in table \ref{systems}.  Notice that the enotes data is quite similar to the original translations,
obtaining a BLEU score of 52.3 when compared against the original text.  Our goal is to produce paraphrases which make many changes to the input, therefore
in the remainder of this paper, we focus our evaluation on the Sparknotes data for evaluation.

Two main trends emerge from figure \ref{bleupinc}.  First, notice that all of the systems which are trained using parallel text achieve higher BLEU scores than the baseline
of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making significant changes to the 
input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are learned using Minimum Error Rate training
tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, but not seeing any BLEU improvements on the test data.  Finally
we note that using the larger language model seems to yield a slight improvement in BLEU score.

\begin{table}
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training instead of using the default Moses parameters.\\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakesperean language model. a\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakesperean Paraphrase.  Romeo and Juliet is held out for testing.}
  \label{systems}
\end{table}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=2.4in]{figures/bleupinc1.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.}
  \label{bleupinc}
\end{figure}

Several example paraphrases generated by our system, both from Romeo and Juliet and several Hollywood movies are presented in table \ref{examples}.

\begin{table}
  \begin{tabular}{|l|l|}
    \hline
    Source & Input & Output \\
    \hline
    \hline
    Romeo \& Juliet & & \\
    Star Wars & & \\
    \hline
  \end{tabular}
\end{table}
